Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-04 inc/hardware/deflector/deflector.tex
merge andreas' comments on the deflector

In order to redirect the beam down the column, custom large area deflector plates were employed in conjunction with the gross accelerator alignment mechanism described earlier.
Four plates are arranged on a hollow tube with a square profile, one on each side.
One of each pair is held at ground while the other has a variable potential.
By varying each potential the beam may be turned in flight.

>>>>

In order to direct the beam down the column, custom large area deflector plates are employed in conjunction with the gross accelerator alignment mechanism described earlier.
Four plates are arranged on a hollow tube with a square profile, one on each side.
One of each pair is held at ground while the other has a variable potential.
By varying each potential the beam may be turned in flight.
